Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-07 WSSSPE1_report/WSSSPE1_summary_report.tex
Section 3 Keynote:  Minor changes and introduce line breaks.

Fernando Perez emphasize that ``open source is reproducible by necessity''
- since reproducibility is a prerequisite for remote collaboration.
Smith therefore defined GitHub as part of the next stage in web
development, following on from the social web of
Facebook et al.: ``The Collaborative Web.''

>>>>

Fernando Perez emphasized that ``open source is reproducible by
necessity'' - since reproducibility is a prerequisite for remote
collaboration.  Smith therefore defined GitHub as part of the next
stage in web development, following on from the social web of
Facebook, i.e., ``The Collaborative Web.''
